---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# strava

<!-- badges: start -->
[![R-CMD-check](https://github.com/tyluRp/strava/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tyluRp/strava/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of strava is to access the strava API from R.

## Authenticate

Create an API application from your personal strava account, read more here: https://developers.strava.com/docs/getting-started/

Then store the following credentials in your `.Renviron` file that you can find with `usethis::edit_r_environ`:

* `STRAVA_ID`
* `STRAVA_SECRET`

Refresh your R session and make a request:

```{r}
library(strava)

if (interactive()) get_athlete_activities()
```

The first time you make a request, you will be asked to authorize. After authorization, the token will be cached in memory for future requests in the current session.
